State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2015-11-12 draft.tex
edits to introduction

Robust model predictive control (RMPC) methods compute control laws for uncertain systems that optimise a 
performance criterion for all possible realisations of the uncertainties.
%
Introduced by~\cite{Witsenhausen:1968} the RMPC problem is formulated as a sequence of games, the
adversary maximises the effect the disturbance has on the objective and the controller solves the optimal
control problem for the worst-case system.
%
We discuss the \emph{closed-loop setup}, i.e. at each stage along the horizon the adversary tries to perturb the system
in a way that produces the maximal stage cost and cost-to-go, the controller computes the minimiser for each stage
reacting at each stage to the disturbance.
%
Algorithmically the closed-loop setup covers the \emph{open-loop setup}, where the disturbance is allowed to perturb the 
entire trajectory before the controller is allowed to react, since this can be understood as a horizon one closed loop
problem for a higher order system.
%
One major challenge in RMPC is to guarantee feasibility of the problem for all possible uncertainties in 
presence of state constraints.
%
This can be achieved by introducing specifically designed constraints in such a way that at the
end of the control horizon the system state is contained in a set that is feasible and invariant for all
possible realisations of uncertainty and for a given feedback controller, in particular the largest such set, 
the so called \emph{maximal robust positive invariant} (MRPI) set.
%
Although this concept was introduced by several authors~\cite{Bertsekas:1971,Glover:1971} shortly after robust 
model predictive control was proposed and analytical properties of MRPI sets were analysed, algorithms for numerically 
computing MRPI sets were introduced over two decades later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}.
%
Earlier algorithms either failed to guarantee finite determinability of the MRPI set, see e.g.~\cite{Blanchini:1990}, 
or were not guaranteed to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}.

>>>>

Robust model predictive control (RMPC) methods compute control laws for uncertain systems that optimise a 
performance criterion for all possible realisations of model uncertainty.
%
Introduced by~\cite{Witsenhausen:1968} the min-max RMPC problem is formulated as a sequence of games in which an
adversary maximises the effect model of uncertainty on a performance objective and the controller solves the optimal
control problem for the resulting worst-case system.
%
We discuss the \emph{closed-loop setup}, i.e. at each stage along the horizon the adversary tries to perturb the system
in a way that produces the maximal stage cost and cost-to-go, the controller computes the minimiser for each stage
reacting at each stage to the disturbance.
%
Algorithmically the closed-loop setup covers the \emph{open-loop setup}, where the disturbance is allowed to perturb the 
entire trajectory before the controller is allowed to react, since this can be understood as a horizon one closed loop
problem for a higher order system.
%
One major challenge in RMPC is to guarantee feasibility of the problem for all possible uncertainties in 
presence of state constraints.
%
This can be achieved by introducing specifically designed constraints in such a way that at the
end of the control horizon the system state is contained in a set that is feasible and invariant for all
possible realisations of uncertainty and for a given feedback controller, in particular the largest such set, 
the so called \emph{maximal robust positive invariant} (MRPI) set.
%
Although this concept was introduced by several authors~\cite{Bertsekas:1971,Glover:1971} shortly after robust 
model predictive control was proposed and analytical properties of MRPI sets were analysed, algorithms for numerically 
computing MRPI sets were introduced over two decades later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}.
%
Earlier algorithms either failed to guarantee finite determinability
of the MRPI set, see e.g.~\cite{Blanchini:1990}, 
or were not guaranteed to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}.
